Pillar 1 - Conformal Prediction

### 2019-06-27 Conference/COPA2019/paper/conference figures COPA2019.Rmd
no message

---
title: "Figures for conference paper"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

# Set up

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)
library(DiagrammeR)

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")
load("Output/conformal.RDATA")

output_folder <- "Conference/COPA2019/paper/figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

```{r latex_table}
latex_table <- function(df, filename = "test"){

  df %>%
    kable("latex", booktabs = TRUE, align = "c") %>%
    write(file = str_c(output_folder, "/", filename, ".txt"))
}
```

```{r TM}
gamma <- app_model$Gamma[[1]]
beta  <- app_model$Beta[[1]]
```

```{r student_data}
set.seed(2019)

student_data <- d_transcript_augmented %>%

  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%

  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization

  sample_n(10) %>%

  arrange(`Academic Year`) %>%

  print
```

```{r course_data}
course_data <- d_text$catalogues %>%

  slice(50005:50014) %>%

  select(`Course ID`, `Course Title`, Department = department, word) %>%

  print
```

# Student data

```{r fig_student_data}
student_data %>% latex_table("data-student")
```

# Course data

```{r fig_course_data}
course_data %>% latex_table("course-student")
```

# Flow chart

## EDM2019 style
```{r}
grViz("digraph flowchart{

      fontname = Helvetica
      size = 15

      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]

      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_input {
		  color = white;

      subgraph cluster_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;

      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      } #close input subgraph

      subgraph cluster_model_fitting{
      label = 'Model Fitting';
      style = filled;
		  color = LavenderBlush;

      SM [label = 'Student Model']

      PM [label = 'Predictive Models']
      x1 [shape = circle, width = .01, height = .01, label = '']
      TM [label = 'Topic Model']

      }

      subgraph cluster_inter_last{
      label = 'Intermediate Results';
      style = filled;
		  color = Tan;

      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;

      SUG [label = 'Course Suggestions']
      PR [label = 'Prediction Region']
      }

      TR [label = 'Student´s Transcript']

      # Invisible node
      x2 [shape = circle, width = .01, height = .01, label = '']
      x3 [shape = circle, width = .01, height = .01, label = '']

      # edges

      {SD, TM} -> SM;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> PR [label = '  Conformal Prediction'];

      CD -> TM [label = '  LDA'];

      SM -> PM [label = '  Lasso'];

      {TM, AI} -> x2 [arrowhead = none]
      x2 -> SUG [label = '  KL distance'];

      }
      ")

# Save by hand
# File name: Conference/COPA2019/paper/figures/flowchart
```

## 2 pillar style
```{r}
grViz("digraph flowchart{

      fontname = Helvetica
      size = 15
      newrank = true;

      node [fontname = Helvetica, shape = rectangle, style = filled, fillcolor = white]
      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_input_kw {
      label = 'User Input';
      penwidth = 2;

      KW [label = 'Selected Key Words']
      }

      subgraph cluster_data {
      label = 'Data';
      penwidth = 2;

		  node [shape = cylinder];
      SD [label = 'Student Data', group = 2]
      CD [label = 'Course Data' , group = 1]
      }

      subgraph cluster_input_course {
      label = 'User Input';
      penwidth = 2;

      CS [label = 'Selected Courses']
      }

      subgraph cluster_pillar_1{
      label = 'Pillar 1: Course Suggestion';
      penwidth = 2;

      TM  [label = 'Topic Model \nof the Courses', group = 1]
      AI  [label = 'Model of \nStudent´s Academic Interests']
      x1  [shape = circle, width = .01, height = .01, label = '']
      SUG [label = 'Course Suggestions', ]

      } # close pillar 1

      subgraph cluster_pillar_2{
      label = 'Pillar 2: Warning Issuance';
      penwidth = 2;

      SM  [label = 'Student Model'    , group = 2]
      PM  [label = 'Predictive Models', group = 2]
      GP  [label = 'Point Prediction \nfor Grade' , group = 2]
      WAR [label = 'Warning'          , group = 2]
      PR  [label = 'Prediction Region', color = red, fontcolor = red]

      } # close pillar 2

		  { rank=same; KW; CD; SD; CS}
		  { rank=same; TM; SM}
      { rank=same; PR; WAR; SUG}

      # edges
      CD -> TM [label = '  LDA'];
      {TM, KW} -> AI;
      {TM, AI} -> x1 [arrowhead = none]
      x1 -> SUG [label = '  KL distance'];

      SD -> SM;
      TM -> SM;
      SM -> PM [label = '  Lasso'];
      {PM, CS} -> GP;
      GP -> WAR;
      GP -> PR [label = ' Conformal Prediction', color = red, fontcolor = red];

      }
      ")

# Save by hand
# File name: Conference/COPA2019/paper/figures/flowchart
```

# Model Selection (topic model)

```{r}
max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]

df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
  geom_line(linetype = "dashed") +
  geom_point() +

  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +

  ggsave(filename = str_c("model-selection.jpeg"), path = output_folder,
         width = plot_width, height = plot_height)
```

# Beta

```{r reorder_within}
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

```{r plot_beta}
plot_beta <- function(topic = 1, resize_factor = 1){

  top <- str_c("Topic ", topic)

  beta %>%
    filter(topic %in% top) %>% 
    group_by(topic) %>%
    top_n(9, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder_within(term, beta, topic), y = beta)) +

    coord_flip() +

    theme(axis.text.y = element_text(size = 11)) +

    labs(title = NULL, x = "Terms", y = "Beta") +

    facet_wrap( ~ topic, scales = "free_y") +
    scale_x_reordered()

  ggsave(filename = "beta.jpeg", path = output_folder,
         width = 1.5 * plot_width / resize_factor, height = plot_height / resize_factor)

}
```

# Gamma

```{r plot_gamma}
plot_gamma <- function(course = "COR1002"){

  gamma %>%
    filter(document == course) %>% 
    top_n(10, gamma) %>%

    ggplot() +
    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +

    coord_flip() +

    labs(title = NULL,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma-", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

}
```

```{r fig_gamma}
plot_gamma("COR1004")

resize_factor <- 1.8

plot_beta(c(4,19), resize_factor = resize_factor)
```

# Topic Expertise
```{r}
courses <- paste("Course", 1 : 3)

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2))

gamma <- tibble(Course    = courses,
                `Topic 1` = c(0  , 0.2, 0  ),
                `Topic 2` = c(0.7, 0.2, 0.4),
                `Topic 3` = c(0.2, 0.2, 0.2),
                `Topic 4` = c(0.1, 0.2, 0.1),
                `Topic 5` = c(0  , 0.2, 0.2))

df1 <- gamma %>% 
  gather(key = Topic, value = gamma, -Course) %>% 
  arrange(Course) %>%

  left_join(transcript, by = "Course") %>%
  mutate(contribution = Grade/10 * gamma)

topic_expertise <- df1 %>%
  select(-gamma, - Grade)%>% 
  spread(key = Topic, value = contribution) %>%
  add_row(Course = "Total", `Topic 1` = 0.18, `Topic 2` = 0.68, `Topic 3` = 0.34, `Topic 4` = 0.26, `Topic 5` = 0.22)

# Table

transcript %>% 
  mutate(Grade = str_c(Grade, "/10")) %>%
  latex_table("toy-transcript")

gamma %>% latex_table("toy-gamma")

topic_expertise %>% latex_table("toy-contribution")

# Plot
df1 %>% 
  mutate(Topic = factor(Topic, levels = str_c("Topic ", 5:1))) %>%
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  coord_flip() +
  labs(x = "Topics", y = "Topic Expertise")

ggsave(filename = str_c("toy-expertise.jpeg"), path = output_folder,
       width = plot_width, height = plot_height)
```

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.y = element_line(color = "white"),
        axis.text.y  = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid   = element_line(color = "white")
        ) +

  labs(y = "Cross-Validation Mean Absolute Error") +
  coord_flip()

ggsave(filename = str_c("cv-mae.jpeg"), path = output_folder,
         width = plot_width/1.5, height = plot_height/3.5)

fit_lasso %>%
  summarize(Mean = mean(cv_error),
            `Weighted mean` = weighted.mean(cv_error, n),
            Median = median(cv_error),
            `Standard Deviation` = sd(cv_error),
            Minimum = min(cv_error),
            Maximum = max(cv_error)) %>%
  gather(key = x, value = y) %>% 
  kable("latex", booktabs = TRUE, col.names = NULL) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/cv-mae-table.pdf"))
```

# Conformal

## course table

```{r}
course_table %>%
  select(- df) %>%
  mutate(cv_error = cv_error %>% round(2)) %>%
  latex_table("conformal-course")
```

## width

```{r}
d_width <- conformal_results %>%
  group_by(course, significance) %>%
  summarise(q_50 = quantile(width, 0.5), # median
            q_10 = quantile(width, 0.1),
            q_90 = quantile(width, 0.9))
```

```{r}
d_width %>%
  ggplot() +
  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(aes(significance, q_50, group = 1)) +
  geom_point(aes(significance, q_50)) +
  facet_wrap( ~ course) +
  labs(y = "Width",
       x = "Significance Level") +
  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))

ggsave(filename = "conformal-width.jpeg", path = output_folder,
       width = plot_width, height = plot_height)
```

## Error

```{r}
d_error <- conformal_results %>%
  group_by(course, significance) %>%
  summarise(error = mean(!hit))
```

```{r}
d_error %>%
  ggplot(aes(x = significance, y = error)) +
  geom_abline(slope = 1, linetype = "longdash") +
  geom_line(aes(group = 1)) +
  geom_point() +
  facet_wrap( ~ course) +
  labs(y = "Error Rate",
       x = "Significance Level") +
  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))

ggsave(filename = "conformal-error.jpeg", path = output_folder,
       width = plot_width, height = plot_height)
```

## Table
```{r}
conformal_results %>%
  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
  group_by(course, significance) %>%
  summarize(width_med  = median(width),
            error_rate = mean(!hit)) %>%

  gather(key = "measure", value = "output", width_med, error_rate) %>%
  mutate(output = round(output, 2)) %>%
  unite(id, measure, significance, sep = "-") %>%
  spread(key = id, value = output) %>%

  select(course, matches("med"), matches("error")) %>%
  latex_table("conformal-table")
```

>>>>

version https://git-lfs.github.com/spec/v1
oid sha256:9c3233bc067a993bccdab77bc21d030f1b3dfe90f2382d90d157a85083c0ac99
size 13510

### 2019-06-27 Conference/EDM2019/conference figures EDM2019.Rmd
no message

---
title: "Figures for conference paper"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

# Set up

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)
library(DiagrammeR)

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

output_folder <- "Conference/Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

```{r TM}
gamma <- app_model$Gamma[[1]]
beta  <- app_model$Beta[[1]]
```

```{r student_data}
set.seed(2019)

student_data <- d_transcript_augmented %>%

  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%

  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization

  sample_n(10) %>%

  arrange(`Academic Year`) %>%

  print
```

```{r}
course_data <- d_text$catalogues %>%

  slice(50005:50014) %>%

  select(`Course ID`, `Course Title`, Department = department, word) %>%

  print
```

# Student data

```{r fig_student_data}
student_data %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/student_data.pdf"))
```

# Course data

```{r fig_course_data}
course_data %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/course_data.pdf"))
```

# Flow chart

```{r}
grViz("digraph flowchart{

      fontname = Helvetica
      size = 15

      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]

      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;

      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      subgraph cluster_model_fitting{
      label = 'Model Fitting';
      style = filled;
		  color = LavenderBlush;

      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']

      PM [label = 'Predictive Models']
      x1 [shape = circle, width = .01, height = .01, label = '']
      TM [label = 'Topic Model']

      }

      subgraph cluster_inter_last{
      label = 'Intermediate Results';
      style = filled;
		  color = Tan;

      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;

      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Courses']
      }

      TR [label = 'Student´s Transcript']

      # Invisible node
      x2 [shape = circle, width = .01, height = .01, label = '']
      x3 [shape = circle, width = .01, height = .01, label = '']

      # edges

      SD -> AP [weight = 2];
      {SD, TM} -> TE;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

      CD -> TM [label = '  LDA'];

      {AP, TE} -> x1 [arrowhead = none]
      x1 -> PM [label = '  Lasso'];

      {TM, AI} -> x2 [arrowhead = none]
      x2 -> SUG [label = '  KL distance'];

      {TM, PM} -> x3 [arrowhead = none]
      x3 -> PRE [label = '  KL distance'];

      }
      ")

# Save by hand
# image format: JPEG
# Width: 626
# Check Maintain aspect ratio
# File name: Conference/Figures/Flowchart
```

# Model Selection (topic model)

```{r}
max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]

df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
  geom_line(linetype = "dashed") +
  geom_point() +

  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +

  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
         width = plot_width, height = plot_height)
```

# Beta

```{r plot_beta}
plot_beta <- function(topic = 1, resize_factor = 1){

  top <-  str_c("Topic ", topic)

  beta %>%
    filter(topic == top) %>% 
    top_n(10, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder(term, beta), y = beta)) +

    coord_flip() +

    theme(axis.text.y = element_text(size = 11)) +

    labs(title = str_c("Topic ", topic),
         x = "Terms",
         y = "Beta"
         )

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

}
```

```{r fig_beta}
plot_beta(1)
```

# Gamma

```{r plot_gamma}
plot_gamma <- function(course = "COR1002"){

  gamma %>%
    filter(document == course) %>% 
    top_n(10, gamma) %>%

    ggplot() +
    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +

    coord_flip() +

    labs(title = course,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

}
```

```{r fig_gamma}
plot_gamma("COR1004")

resize_factor <- 1.6

plot_beta(4, resize_factor = resize_factor)
plot_beta(19, resize_factor = resize_factor)
```

# Topic Expertise
```{r}
courses <- paste("Course", 1 : 3)

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2.5))

gamma <- tibble(Course    = courses,
                `Topic 1` = c(0  , 0.2, 0  ),
                `Topic 2` = c(0.7, 0.2, 0.4),
                `Topic 3` = c(0.2, 0.2, 0.2),
                `Topic 4` = c(0.1, 0.2, 0.1),
                `Topic 5` = c(0  , 0.2, 0.2))

df1 <- gamma %>% 
  gather(key = Topic, value = gamma, -Course) %>% 
  arrange(Course) %>%

  left_join(transcript, by = "Course") %>%
  mutate(contribution = Grade/10 * gamma)

topic_expertise <- df1 %>%
  select(-gamma, - Grade) %>% 
  spread(key = Topic, value = contribution)

# Table

transcript %>% 
  mutate(Grade = str_c(Grade, "/10")) %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))

gamma %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))

topic_expertise %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  labs(x = "Topics", y = "Topic Expertise")

ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
       width = plot_width, height = plot_height)
```

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.y = element_line(color = "white"),
        axis.text.y  = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid   = element_line(color = "white")
        ) +

  labs(y = "Cross-Validation Mean Absolute Error") +
  coord_flip()

ggsave(filename = str_c("CV.jpeg"), path = output_folder,
         width = plot_width/1.5, height = plot_height/3.5)

fit_lasso %>%
  summarize(Mean = mean(cv_error),
            `Weighted mean` = weighted.mean(cv_error, n),
            Median = median(cv_error),
            `Standard Deviation` = sd(cv_error),
            Minimum = min(cv_error),
            Maximum = max(cv_error)) %>%
  gather(key = x, value = y) %>% 
  kable("latex", booktabs = TRUE, col.names = NULL) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/CV.pdf"))
```

>>>>

version https://git-lfs.github.com/spec/v1
oid sha256:acf1a764242de21f44aed1b7332583505cf243fabd0e5d22e18520d426f1bf59
size 8680

### 2019-06-27 Pillar 1 - Conformal Prediction.Rmd
no message

---
title: "Pillar 1 - Conformal Prediction"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Set up

```{r setup, include = FALSE}
set.seed(1)

knitr::opts_chunk$set(fig.width = 3, fig.height = 2,
                      echo = FALSE, warning = FALSE)

library(tidyverse)
library(glmnet)

load("Output/CV.RDATA")
load("Output/data_student.RDATA")
load("Output/student_profile.RDATA")
```

```{r setup_graph}
theme_set(theme_light())

output_folder <- "Conference/COPA2019/paper/figures"
plot_width  <- 6
plot_height <- plot_width / 1.6 
```

# Course selection
I select courses with large and small n, and large and small CV error. I do not select courses whose lasso model contains less than 3 non-zero coefficients (df).

* COR1002: large n
* COR1004: large n and smaller CV error (mean absolute error) than COR1002

* SCI3003: small n and large CV error
* SCI2040: small n and small CV erro

* SSC3044: small CV error
* SSC3038: small CV error and n twice as large as SSC3044

* SCI2018: large CV error
* SCI2010: large CV error and n twice as large as SCI2018

```{r course_selection}
course_selection <- c(
#  "SCI3003", "SCI2040", # remove because n too small
  "COR1002", "COR1004",  "SSC3044", "SSC3038", "SCI2018", "SCI2010")

course_table <- fit_lasso %>% 
  filter(target %in% course_selection) %>% 
  select(target, n, cv_error, df)
```

# Conformal Prediction setp by step

## Cross-validation

```{r CV helper}
create_Z <- function(course){

  student_profile %>%
    filter(`Course ID` == course) %>%
    select(Y = Grade, matches("GPA|Topic"))

}

add_fold <- function(df, n_fold = 10){

  n         <- nrow(df)
  fold_size <- ceiling(n / n_fold)
  folds     <- rep(1 : 10, fold_size) %>% sample %>% .[1 : n]

  df %>% mutate(fold = folds)

}
```

## Training, callibration and test sets

```{r split helper}
create_test <- function(df, fold_current) df %>% filter(fold == fold_current)

create_training <- function(df, fold_current) df %>% filter(fold != fold_current)

add_allocation <- function(df){

  n_training <- nrow(df)
  n_proper_training <- floor(0.67 * n_training)        # 2/3
  n_calibration     <- n_training - n_proper_training  # 1/3

  allocation <- rep(x     = c("proper training", "calibration"), 
                    times = c(n_proper_training, n_calibration)) %>%
  sample

  df %>% mutate(allocation = allocation)

}

create_proper_training <- function(df) df %>% filter(allocation == "proper training")

create_calibration     <- function(df) df %>% filter(allocation == "calibration")
```

## Fit lasso on training set
```{r,lasso helper}
fit_target_model <- function(df){

  X <- df %>% select(matches("GPA|Topic"))
  Y <- df %>% pull(Y)

  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default. Use mean absolute error

}

predict_grade <- function(df, model){

  X <- df %>% select(matches("GPA|Topic"))

  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min") # use lambda that minimizes mae

  df %>% mutate(Y_hat = as.vector(Y_hat),
                error = abs(Y_hat - Y),
                mu    = log(error)) # take ln of absolute error

}

fit_error_model <- function(df){

  X  <- df %>% select(matches("GPA|Topic"))
  mu <- df %>% pull(mu)

  cv.glmnet(x = as.matrix(X), y = mu, type.measure = "mae")

}

predict_error <- function(df, model){

  X <- df %>% select(matches("GPA|Topic"))

  mu_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")

  df %>% mutate(mu_hat = as.vector(mu_hat))

}
```

## Compute standardized non-conformity scores on callibration test
```{r}

compute_ncs              <- function(df) df %>% mutate(alpha = abs(Y - Y_hat))

compute_standardized_ncs <- function(df) df %>% mutate(sigma = exp(mu_hat),
                                                       alpha = abs(Y - Y_hat) / sigma )

compute_significance     <- function(df) df %>% mutate(significance = rank(-alpha) / nrow(.) ) # !!! double check!!!
```

## Evaluate error rate on test set

```{r}
compute_width <- function(df, significance_given){

  df <- df %>% filter(significance <= significance_given)

  min(df$alpha)

}

compute_interval <- function(df, ncs){

  df %>% mutate(
    sigma       = exp(mu_hat),
    width       = ncs * sigma,
    border_low  = Y_hat - width,
    border_high = Y_hat + width
    )
}

compute_hit <- function(df){
  df %>% mutate(hit = (border_low <= Y) & (Y <= border_high))
}
```

# Loop through all courses

```{r, echo = FALSE}

# Set up

significance <- c(0.05, seq(0.1, 0.9, 0.1))
results <- list()
n_list <- 1

for(course in course_selection){

  # data
  Z <- create_Z(course)
  Z <- add_fold(Z)

  for(iteration in 1 : 10){

    # proper training, calibration and test sets
    Z_test            <- create_test(Z, fold_current = iteration)
    Z_training        <- create_training(Z, fold_current = iteration) %>% add_allocation
    Z_proper_training <- create_proper_training(Z_training)
    Z_calibration     <- create_calibration(Z_training)

    # fit target and error model to proper training set
    model_target      <- fit_target_model(Z_proper_training)
    Z_proper_training <- predict_grade(Z_proper_training, model_target)
    model_error       <- fit_error_model(Z_proper_training)

    # non-conformity scores on calibration
    Z_calibration <- Z_calibration %>% 
      predict_grade(model_target) %>%
      predict_error(model_error) %>%
      compute_standardized_ncs %>%
      compute_significance

    # error on test set
    Z_test <- Z_test %>% 
      predict_grade(model_target) %>%
      predict_error(model_error)

    for(signi in significance){ # loop through significance levels

      ncs <- compute_width(Z_calibration, signi)

      Z_test_augmented <- Z_test %>% 
        compute_interval(ncs = ncs) %>%
        compute_hit

      # save results
      results[[n_list]] <- Z_test_augmented %>%
        mutate(significance = signi,
               iteration    = iteration,
               course       = course) %>%
        select(course, iteration, significance, width, hit,
               Y, Y_hat, error, mu, mu_hat, sigma)

      n_list <- n_list + 1

    } # end loop significance

  } # end CV fold

}
```

```{r}
conformal_results <- bind_rows(results) %>%
    mutate(iteration    = as.factor(iteration),
           course       = as.factor(course))

save(conformal_results, course_table, file = "Output/conformal.RDATA")
```

Illustration of the effect of error_hat on interval's width (for significance of 99%):
```{r, fig.height=4}
Z_test %>% select(Y, Y_hat, error, error_hat, width, border_low, border_high, hit)
plot(Z_test$error, Z_test$error_hat)
```

Correlation between the actual errors and the predicted errors (error_hat):
```{r}
cor(Z_test$error, Z_test$error_hat)
```

```{r, echo = FALSE, eval = F}
ggplot(data = Z_callibration) + geom_histogram(aes(Y), bins = 15)

ggplot(data = Z_callibration) + geom_histogram(aes(Y_hat), bins = 15)

ggplot(data = Z_callibration) + geom_histogram(aes(alpha), bins = 15)
```

```{r, echo = FALSE, eval = F}
ggplot(data = Z_callibration) + geom_point(aes(Y, Y_hat))

ggplot(data = Z_callibration) + geom_point(aes(Y, alpha))

ggplot(data = Z_callibration) + geom_point(aes(Y_hat, alpha))
```

>>>>

version https://git-lfs.github.com/spec/v1
oid sha256:1695b735cec1287d29ba5b74efc8cd72caa362611bd81c9a7b5d5a1855ab484d
size 7419
